\section{Introduction}
Pricing is at the core of Walmart shopping experience. An important part of maintaining customer trust in Walmart is to 
provide customers with consistent prices on items across the box in line with EDLP (Everyday low price) principles.

Merchants are faced with the task of making pricing decisions on a daily basis. One of the major challenges 
faced by merchants is to identify impact of price changes on unit sales of an item and predicting corresponding 
demand owing to different pricing scenarios. Currently, merchants do not have a consistent system or process for 
evaluating the impact of pricing decisions. Merchants often rely on input from suppliers and/or institutional knowledge. 
To tackle this challenge, machine learning techniques has been used to design a solution to provide visibility to 
the expected unit volume change of an item and items affected by cross-price elasticity in response to a price change. 
The solution has been proposed to facilitate data driven decision making on pricing to achieve desired business objectives.

Accuracy of demand equation for each UPC achieved by machine learning techniques has been evaluated using out of 
time testing with MAPE (mean average percentage error) as an evaluation metric.

Rest of the paper has been organized as follows: Section II describes the data used, formulation of the demand 
equation and simulation approach for calculating elasticity estimates. Section III includes explanation of features 
for modelling exercise and modelling techniques. Section IV and V describes model results and evaluation and Section VI 
provides salient conclusion of the work.
