\section{Problem}
\label{sec:prob}

In this section we introduce our threat model, as well as all
assumptions we make about the environment. We defer all discussion
about our assumptions and threats to the validity of our research to
Section~\ref{sec:disc}. Given our threat model and assumptions, we then
define the problem statement this work aims to solve at the end of this
section. 

\myparagraph{Threat Model} This work considers an adversary performing
active reconnaissance from a compromised switch, in a software defined
network. Further, it is assumed at most one switch within the network 
is compromised for the entirety of the attack, nor is the compromised 
switch a core switch in the network. This assumption prevents an 
adversary from maintaining a passive view of the entire network and 
forces the adversary to perform active reconnaissance to get a complete
view of the network. The adversary not only has the ability to 
compromise the switch, but is also capable of crafting spoofed packets
at the switch, which result in illegitimate packet\_in messages to be 
sent to the controller and be processed by the applications in the 
application plane. In addition, the adversary is capable of ignoring 
flow\_mod messages and dropping packets matching a specific flow, 
particularly to prevent their spoofed packet from propagating throughout
the network. Finally, the adversary maintains full knowledge of our 
solution and the algorithms used to detect reconnaissance activity. 
With these stated capabilities, the adversary aims to gather 
intelligence about the network, which is later used to form an attack
plan to exfiltrate data from sensitive resources inside the network.

We define our Trusted Computing Base (TCB) to be the SDN controller and
applications as well as the communication channels used by the North
Bound and South Bound Interfaces, note only the channels are trusted and
not the data relayed within the channels. That is to say we guarantee
which switch is actually sending data but we don't trust what that data
actually reports. Our assumed environment is a fully SDN enabled 
enterprise network, whose topology was configured using well known best 
practices.

\myparagraph{Problem Statement} \textit{Software Defined Networks
introduce a new perspective, for adversaries controlling a compromised
switch, to perform sophisticated and stealthy network reconnaissance.
Detecting such network reconnaissance techniques is crucial to the
security of the network, since the information gathered may be used to
launch devastating attacks against the network.}
